HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
background edits

The Abstract Meaning Representation (AMR) scheme \cite{banarescu2013abstract}
shares much of UCCA's motivation for defining a more complete semantic annotation.
However, using AMR is not optimal for defining a decomposition of a sentence into semantic
units as it does not ground its semantic symbols in the text,
thus not straightwardly allowing a decomposition of the sentence into sub-units.
Moreover, AMR is more fine-grained than UCCA and consequently more difficult to annotate.
Other approaches pursued a grounded representation of semantics,
and have generally represented semantic structures as bi-lexical dependencies.
Examples include the tectogrammatical layer \parcite{sgallhp:1986} used in the Prague dependency
treebanks, e.g. the Czech-English one \parcite{hajic2012announcing}, as well
as dependencies derived from Minimal Recursion Semantics representations \parcite{oepen2006discriminant}.
Nevertheless, despite their appeal as deep and intuitive means for semantic representation,
these approaches require linguistic expertise for their annotation, due to the intricate and
fine-grained distinctions they provide, and are thus in our view less suitable for basing
an interpretable MT evaluation on.

>>>>

The Abstract Meaning Representation (AMR) scheme \cite{banarescu2013abstract}
shares much of UCCA's motivation for defining a more complete semantic annotation.
However, using AMR is not optimal for defining a decomposition of a sentence into semantic
units as it does not ground its semantic symbols in the text,
thus does not provide clear decomposition of the sentence into sub-units.
Also, AMR is more fine-grained than UCCA and consequently more difficult to annotate.
Other approaches pursued a grounded representation of semantics,
and have generally represented semantic structures as bi-lexical dependencies.
Examples include the tectogrammatical layer \parcite{sgallhp:1986} used in the Prague dependency
treebanks, e.g. the Czech-English one \parcite{hajic2012announcing}, as well
as dependencies derived from Minimal Recursion Semantics representations \parcite{oepen2006discriminant}.
Nevertheless, despite their appeal as deep and intuitive means for semantic representation,
these approaches require linguistic expertise for their annotation, due to the intricate and
fine-grained distinctions they provide, and are thus in our view less suitable for basing
an interpretable MT evaluation on.
